### 2017-02-08 Conclusion/Conclusion.tex
Some more updates

\chapter{Conclusions and outlook}
\label{chap:conclusions}
In this thesis analyses of proton-proton collisions recorded by the \ac{CMS} detector during
Run 1 and Run 2 of the \ac{LHC} have been presented.
The search for a heavy Higgs boson decaying to a final state of $bb\Pgt\Pgt$ via two
125 GeV Higgs bosons was performed using 19.7 fb$^{-1}$ collected at a
centre of mass energy of 8 TeV during the 2012 \ac{LHC} data-taking period. Such a final
state can access areas of the MSSM phase space not easily accessible via other channels.
The results of this search are upper limits on production cross section times branching 
ratio, in a mass range $260<m_H<350$ GeV. A combination with a search for \AtoZhtolltautau
yields exclusion in the lowest \tanb~region of the low-tanb~MSSM scenario, as well
as several areas of the \cosba-\tanb~plane in a \ac{2HDM} scenario.

Searches for a heavy neutral Higgs boson decaying into pairs of tau leptons were performed
using 2.3 fb$^{-1}$ of proton-proton collision data recorded during the 2015
data-taking period of the \ac{LHC}, and using 12.9 fb$^{-1}$ of proton-proton collision
data recorded during the first half of the 2016 data-taking period.
No significant excess is observed, and so these analyses set limits on the production cross section times branching ratio of both the
gluon fusion and b-associated production processes. The results are also
interpreted in MSSM benchmark scenarios, where the analyses exclude large areas
of the \mA-\tanb~plane, with significant improvement with respect to the most sensitive
results obtained in Run 1. A combination of the 2015 and 2016 analyses is also
performed. This combination improves on the results of the 2016 analysis alone, thus
setting the most stringent limits on this process to date.

As more data are collected during the rest of Run 2, and in the 
future, searches for MSSM Higgs bosons in the di-$\Pgt$ final
state will continue. If no such Higgs bosons are found, these searches
will be able to exclude even more of the \mA-\tanb~plane in specific
MSSM benchmark scenarios. A projection of the results of the 2015 \ac{MSSM}
analysis to an integrated luminosity of 300 fb$^{-1}$ and 3000 fb$^{-1}$ is
shown in figure \ref{fig:mssm_projection_fig}. Even with an integrated luminosity of
3000 fb$^{-1}$ it is not possible to exclude the full \mA-\tanb~plane of this scenario,
as the branching ratio of $\PHiggsps/\PHiggs$ into di-$\Pgt$ pairs 
is very low in the bottom right corner. This region can be accessed 
via searches for the $\PHiggsps/\PHiggs \rightarrow \Ptop\APtop$ decay, which
has an enhanced branching ratio in this region. To fully cover the still
available phase space it will therefore start to become more and more
important to combine searches for heavy Higgs bosons in different final states.
Doing this will give the best sensitivity to possible
heavy Higgs bosons - or in the absence of these particles exclusion
of the scenarios that predict them.

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.7\textwidth]{./Conclusion/Figures/MSSMProjection.png}
\end{center}
\caption{The expected exclusion in the $m_{h}^{\text{mod+}}$ scenario
 at 95\% CL of the 2015 MSSM analysis (pink)
projected to an integrated luminosity of 300 fb$^{-1}$ (blue) and 3000 fb$^{-1}$ (red)
under several assumptions of how the systematic uncertainties scale. Even with 3000 fb$^{-1}$
not the entire \mA-\tanb~plane in this MSSM benchmark model \cite{HTT-projection}.}
\label{fig:mssm_projection_fig}
\end{figure}

>>>>

\chapter{Conclusions and outlook}
\label{chap:conclusions}
In this thesis analyses of proton-proton collisions recorded by the \ac{CMS} detector during
Run 1 and Run 2 of the \ac{LHC} have been presented. The focus of these analyses
is the search for \ac{BSM} Higgs bosons with tau leptons in the final state.

The search for a heavy Higgs boson decaying to a final state of $bb\Pgt\Pgt$ via two
125 GeV Higgs bosons was performed using 19.7 fb$^{-1}$ of data collected at a
centre of mass energy of 8 TeV during the 2012 \ac{LHC} data-taking period. Such a final
state can access areas of the MSSM phase space not easily accessible via other channels.
To separate more signal-like and more background-like events, a categorisation based on the number of 
b-tagged jets is used. To further increase the sensitivity to the signal, cuts on the di-tau and di-b
mass in a window around 125 GeV are used in combination with a kinematic fitting technique for
the reconstruction of the 4-body mass.
The resulting mass variable provides good separation between the signal and the dominant
\ttbar background, and is thus used as the variable for signal extraction. 
The results of this search are upper limits on production cross section times branching 
ratio, in a mass range $260<m_H<350$ GeV. A combination with a search for \AtoZhtolltautau
yields exclusion in the lowest \tanb~region of the low-tanb~MSSM scenario, as well
as several areas of the \cosba-\tanb~plane in a \ac{2HDM} scenario.

Searches for a heavy neutral Higgs boson decaying into pairs of tau leptons were performed
using 2.3 fb$^{-1}$ of data recorded during the 2015
data-taking period of the \ac{LHC}, and using 12.9 fb$^{-1}$ of 
data recorded during the first half of the 2016 data-taking period. The 
branching ratio of heavy neutral Higgs bosons into di-\Pgt pairs is enhanced at high \tanb~in the \ac{MSSM},
making this one of the most sensitive search channels for such particles. The analysis uses a categorisation 
based on the presence of b-tagged jets to separate
the gluon fusion and b-associated production modes of Higgs bosons in the \ac{MSSM}. 
The hadronic tau isolation working point, as well as the topological selection on 
the \mT~variable, are chosen to optimise the search sensitivity for signal
masses of around 1 TeV.
The sensitivity is maximised by using the \mTtot~variable for signal extraction.
This variable separates the dominant backgrounds
and the high-mass signal well.
No significant excess is observed in these searches, and so 
these analyses set limits on the production cross section times branching ratio of both the
gluon fusion and b-associated production processes. The results are also
interpreted in MSSM benchmark scenarios, where the analyses exclude large areas
of the \mA-\tanb~plane, with significant improvement with respect to the most sensitive
results obtained in Run 1. A combination of the 2015 and 2016 analyses is also
performed. This combination improves on the results of the 2016 analysis alone, thus
setting the most stringent limits on this process to date.

As more data are collected during the remainder of Run 2, and in the 
future, searches for MSSM Higgs bosons in the di-$\Pgt$ final
state will continue. If no such Higgs bosons are found, these searches
will be able to exclude even more of the \mA-\tanb~plane in specific
MSSM benchmark scenarios, although not all of the \mA-\tanb~plane
will become accessible. A projection of the results of the 2015 \ac{MSSM}
analysis to an integrated luminosity of 300 fb$^{-1}$ and 3000 fb$^{-1}$ is
shown in figure \ref{fig:mssm_projection_fig}. Even with an integrated luminosity of
3000 fb$^{-1}$ it is not possible to exclude the full \mA-\tanb~plane of this scenario,
as the branching ratio of $\PHiggsps/\PHiggs$ into di-$\Pgt$ pairs 
is very low in the high \mA-low \tanb~corner. This region can be accessed 
via searches for the $\PHiggsps/\PHiggs \rightarrow \Ptop\APtop$ decay, which
has an enhanced branching ratio in this region. To fully cover the still
available phase space it will therefore start to become more and more
important to combine searches for heavy Higgs bosons in different final states.
Doing this will give the best sensitivity to possible
heavy Higgs bosons - or in the absence of these particles exclusion
of the scenarios that predict them.

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.7\textwidth]{./Conclusion/Figures/scenario_comp2.pdf}
\end{center}
\caption{The expected exclusion in the $m_{h}^{\text{mod+}}$ scenario
 at 95\% CL of the 2015 MSSM analysis (pink)
projected to an integrated luminosity of 300 fb$^{-1}$ (blue) and 3000 fb$^{-1}$ (red)
under several assumptions of how the systematic uncertainties scale. Even with an integrated 
luminosity of 3000 fb$^{-1}$ it is not possible to exclude the entire \mA-\tanb~plane
in this \ac{MSSM} benchmark scenario \cite{HTT-projection}.}
\label{fig:mssm_projection_fig}
\end{figure}

### 2017-02-08 MSSM/MSSM.tex
Some more updates

The basis of the event selection is to select \mutau, \etau,
\tautau and \emu pairs. Events are selected first by using a trigger,
followed by additional selection criteria. For the \etau
and \mutau channels we only trigger on the electron or muon. 
While the lepton + hadronic tau cross triggers that are also available
allow for a 3 (6) GeV lower \pT~threshold on the
muon (electron), the benefit of using such a trigger is small as 
most of the signal samples at high-mass, the region of interest in this
analysis, have higher \pT~electrons and muons. This is illustrated
in figure \ref{fig:mt_muonpt}a, which shows the \pT~of muons in the
\mutau channel, with the signal normalised to 4000 times its cross--section
times branching ratio at \mA=1 TeV and \tanb=50 in the $m_{h}^{\text{mod}+}$ scenario overlaid.
In the \emu channel two dedicated electron-muon cross triggers
are used. These have significantly lower online \pT~cuts 
on the two leptons than the single lepton triggers. For the 
\tautau channel a di-tau cross-trigger is used.

Because the triggers involving electrons or muons reach 
their maximum efficiency as a function of \pT~quickly, the offline \pT~cut
on the electrons and muons is 1 GeV above the \pT~threshold of the trigger. The
hadronic tau efficiency turns on much more slowly, and therefore the offline \pT~cut
on the hadronic taus in the \tautau channel is 5 GeV above the trigger \pT~threshold.
In addition, a requirement is made on the $\eta$ of the electrons, muons and
hadronic taus. Such a selection is driven by the $\eta$ range covered by the tracker and the $\eta$
range that is used in the reconstruction of the particles,
although in some cases the used trigger is restricted in $\eta$ and the cut is chosen to
align with that. As an illustration figure \ref{fig:mt_muonpt}b shows
the $\eta$ distribution for electrons in the \etau channel, again with the signal overlaid.
The signal peaks in the central $\eta$ region.

Other selections include cuts on the impact parameters $d_{xy}$ and $d_{z}$, which
ensure that the particle is compatible with having
originated from the primary vertex. This reduces the selection of particles
coming from pile--up events. Additional identification and isolation criteria
are also applied. These will be discussed in the following sections.
The optimisation of some of the selections will also be discussed there. Note that 
the optimisations were all based on the dataset collected during 2015, which
corresponds to an integrated luminosity of 2.3 fb$^{-1}$.

@@

\subsection{Pair selection and vetos}
\label{sec:mssm_eventsel_pairs}
The basis of the event selection is the selection of \mutau, \etau,
\tautau and \emu pairs by the requirements described
in the following subsections. After applying trigger
requirements, identification criteria and kinematic cuts
more than one possible candidate pair can exist. If
this is the case the pair with the two most isolated candidates
 is chosen, as isolated candidates are less likely 
to be jets misreconstructed
as leptons or hadronic taus.
%If this
%is the case for an event, the pair is chosen as follows:
%\begin{itemize}
%\setlength{\itemsep}{-\baselineskip}
%\item Prefer the pair with most isolated candidate 1 (muon for \mutau and \emu channels,
%electron for \etau channel, either of the $\Pgt_h$s in \tautau channel). For electrons
%and muons this means the object with the smallest relative isolation value is preferred, for $\Pgt_h$s the
%object with raw MVA isolation value nearest to 1.
%\item If the isolation of candidate 1 is the same in both pairs, prefer the pair with highest candidate 1 \pT.
%\item If the \pT~of candidate 1 is the same in both pairs, prefer the pair with most isolated
%candidate 2 (e for the \emu channel, the other $\Pgt_h$ for the \tautau channel, 
%and the $\Pgt_h$ for \etau and \mutau channels).
%\item If the isolation of candidate 2 is the same in both pairs, prefer the pair with highest candidate 2 \pT.
%\end{itemize}

To prevent overlap with other channels, events are rejected
if there are muons and electrons, other than those in the selected pair,
with \pT~$>10$ GeV and passing loose ID and isolation requirements.
This also reduces backgrounds from \WZ events. The application
of these vetos means that the selection of the pair with the
two most isolated candidates is only important where hadronic
taus are concerned, for if there were additional electrons
or muons the event would not pass the electron or muon veto.
In addition to these extra electron and muon vetos, \Zee events are 
reduced in the \etau channel by rejecting events
where an opposite--sign pair of electrons of \pT~$>15$ GeV
and passing very loose ID and isolation requirements can be formed. 
In the \mutau channel the contribution from \Zmm events
is reduced in a similar fashion.

@@

@@

This means that $m_{\text{T}}(E_{\text{T}}^{\text{miss}},\Pgt_1^{\text{vis}})$ is equivalent
to the \mT~defined for the \etau and \mutau channels in equation \ref{eqn:hhh_selection_mt}.
The \mTtot~variable provides good separation between signal and QCD multi--jet events
in the \etau, \mutau and \tautau channels, and between
signal and \ttbar events in the \emu channel. These are some of the 
major backgrounds and thus good separation between these processes and 
the signal is important for the sensitivity of the analysis.
The separation between signal and backgrounds is illustrated in figure
\ref{fig:mttot_sigseps}, where figure \ref{fig:mttot_sigseps} shows the total transverse mass
distribution of the QCD
background in the no b-tag category of the \tautau channel with the gluon fusion
signal at 400 GeV, 1 TeV and 2 TeV overlaid. Figure \ref{fig:mttot_sigseps}b
shows the total transverse mass distribution of the \ttbar background in the b-tag category of the \emu channel with
the b-associated production signal at the same three masses overlaid.

\section{Background estimation}
\label{sec:mssm_bkgs}
There are several backgrounds in this analysis, and the different final
states can have different background compositions. Consider figure \ref{fig:mssm_bkgs_overview}a,
which shows the low $m_{\text{T}}^{\text{tot}}$ region in the no b-tag category
of the \mutau channel and figure \ref{fig:mssm_bkgs_overview}b, which shows the low $m_{\text{T}}^{\text{tot}}$
region in the b-tag category of the \emu channel. These regions are where the backgrounds are concentrated and it
is therefore easier to see the different contributions. \Ztautau is a background in all four channels as 
it has two real taus in the final state, like the signal that we are searching for. The only aspect
that distinguishes the \Ztautau background from the gluon fusion signal is the mass of the particle. Smaller backgrounds
from \Zellell decays also play a role, especially in the \mutau and \etau channels where such events
might pass the selection for example if a jet is misreconstructed as a hadronic tau and only one of the leptons is reconstructed. 
Production of QCD multijet events, labelled QCD on the plots in figure \ref{fig:mssm_bkgs_overview}, is a background when 
two jets are misreconstructed as the two particles of the candidate pair. %Relatively likely to happen in tautau channel
As visible in figure \ref{fig:mssm_bkgs_overview}b, the \ttbar background is particularly important in the b-tag category.
This is because top quarks virtually always decay as $\Ptop\rightarrow \PW\Pbottom$. and so such events 
always contain real b-jets. One or both of the \PW bosons, and additional jets in the event, can 
then form \etau, \mutau, \tautau and \emu pairs.
The \Wjets background arises in the \etau and \mutau channels when the lepton from the \PW decay and a jet misreconstructed
as a hadronic tau form a pair. In the \tautau channel it is a background when the \PW decays into $\Pgt\Pgn$ with the tau 
decaying hadronically and an additional jet in the event is misreconstructed as a hadronic tau, or when two jets are
reconstructed as hadronic taus.
In the \emu channel an additional lepton would have to originate from one of the jets, and so here this
background is smaller. Backgrounds that are small in all channels are the di-boson and single-top backgrounds. In 
figures showing the backgrounds the di-boson and single-top backgrounds are drawn together with the \Wjets 
background as the `Electroweak' component.

@@

To estimate these backgrounds a mixture of data-driven 
methods and \ac{MC} samples is employed. The QCD background
is estimated using data-driven techniques in all four channels.
In the \mutau and \etau channels the \Wjets background is also
estimated using data-driven techniques. The control regions used
in the estimation of QCD and \Wjets in the \etau and \mutau channels
are included in a simultaneous fit with the signal region to obtain
the final results. More detail on this is given in section ADD SECTION.
In the \emu and \tautau channels the \Wjets background is estimated using
\ac{MC} samples. The \Ztautau and \Zellell backgrounds are also estimated
using \ac{MC} samples, and a \Zmm control region
is considered in a simultaneous fit with the signal region to correct and
constrain the \Ztautau normalisation.
The \ttbar, di-boson and single-top backgrounds are estimated
using \ac{MC} samples, with cross-checks in control regions in data.
The rest of this section describes the background estimation methods
in more detail.

@@

\subsubsection{QCD normalisation}
\label{sec:mssm_bkgs_etmt_qcdnorm}
The QCD normalisation is estimated by inverting the opposite-sign requirement
of the di-tau pair in the signal region. The yield is taken from the same--sign
region with otherwise identical cuts to the opposite--sign region. The contributions
from other backgrounds in this region are subtracted to give an estimate of the number
of QCD events in the same--sign region. For all backgrounds apart from \Wjets the
yields to subtract are estimated using \ac{MC} samples. The number of \Wjets events
expected in this region is given by
\begin{equation}\label{eqn:wjets_qcdsub}
N_{\text{W,SS low }m_{\text{T}}} = \frac{N_{\text{MC,SS low }m_{\text{T}}}}{N_{\text{MC,SS high }m_{\text{T}}}}N_{\text{W,SS high }m_{\text{T}}}.
\end{equation}
Because opposite--sign and same--sign QCD events do not
necessarily appear in equal amounts the number of QCD
events obtained by subtracting other backgrounds from the
observed number of events in the same--sign region is multiplied
by $R_{\text{QCD}}^{\text{OS/SS}}$ as derived in section \ref{sec:mssm_bkgs_etmt_qcdosss} 
to obtain an estimate of the number of QCD events in the signal region.

\subsubsection{Control regions in the fit}
\label{sec:mssm_bkgs_etmt_ctrl}
Several control regions in data are used for the estimation
of the QCD and \Wjets backgrounds: the same--sign and 
opposite--sign high \mT~regions, as well as the same--sign
low \mT~region. This leads to three control regions used 
in each category of both the \mutau and \etau channels to determine
the initial estimate of the background normalisations.
These control regions are included in a simultaneous fit
with the signal regions to obtain the final results. More detail
can be found in section \ref{sec:mssm_sigext_ctrl}.

@@

\section{Combination procedure}
\label{sec:mssm_combination_procedure}
The idea of combining the two analyses is to combine the 
individual likelihoods to improve the analysis sensitivity and
physics reach. To do this correctly the correlations between
nuisance parameters in the 2015 and 2016 analyses need to be taken into account.
The correct way to establish the correlations is to perform
dedicated studies into them. In many cases such studies would be 
unfeasible to perform, or it would not be clear how to approach the 
problem in the first place.

Even without performing these studies, a choice of correlation scheme can be motivated
by carefully considering the differences between the two analyses and the conditions
under which they were performed.
This is what has been done for this combination.
%Strictly, studies into the underlying correlations between
%nuisance parameters should be performed. This is however not always
%feasible and in some cases
The correlation scheme between nuisance parameters relating to the 2015 and 2016
analyses, as used for this combination, is given in table \ref{tab:mssm_combination_correlations}. 
The third column of this table gives the motivation for the chosen correlation.

@@

e$\rightarrow\Pgt_{h}$ fake rate & Correlated & Expect to behave the same in 2015 and 2016 datasets.\\

>>>>

The basis of the event selection is to identify \mutau, \etau,
\tautau and \emu pairs. Events are selected first by using a trigger,
followed by additional selection criteria. For the \etau
and \mutau channels we only trigger on the electron or muon. 
While the lepton + hadronic tau cross triggers that are also available
allow for a 3 (6) GeV lower \pT~threshold on the
muon (electron), the benefit of using such a trigger is small as 
most of the signals at high-mass, the region of interest in this
analysis, have higher \pT~electrons and muons. This is illustrated
in figure \ref{fig:mt_muonpt}a, which shows the \pT~of muons in the
\mutau channel, with the signal normalised to 4000 times its cross--section
times branching ratio at \mA=1 TeV and \tanb=50 in the $m_{h}^{\text{mod}+}$ scenario overlaid.
In the \emu channel two dedicated electron-muon cross triggers
are used. These have significantly lower online \pT~cuts 
on the two leptons than the single lepton triggers. For the 
\tautau channel a di-tau cross-trigger is used.

Because the triggers involving electrons or muons reach 
their maximum efficiency as a function of \pT~quickly, the offline \pT~cut
on the electrons and muons is 1 GeV above the \pT~threshold of the trigger. The
hadronic tau efficiency turns on much more slowly, and therefore the offline \pT~cut
on the hadronic taus in the \tautau channel is 5 GeV above the trigger \pT~threshold.
In addition, a requirement is made on the $\eta$ of the electrons, muons and
hadronic taus. This election is driven by the $\eta$ range covered by the tracker and
that is thus used for the reconstruction of the particles. For some of the
channels the used trigger is restricted in $\eta$. If that is the case
then the cut is chosen to align with the trigger restrictions.
As an illustration figure \ref{fig:mt_muonpt}b shows
the $\eta$ distribution for electrons in the \etau channel, again with the signal overlaid.
The signal peaks in the central $\eta$ region.

Other selections include cuts on the impact parameters $d_{xy}$ and $d_{z}$, which
ensure that the particle is likely to have
originated from the primary vertex. This reduces the number of selected particles
which come from pile--up interactions.
Additional identification and isolation criteria
are also applied; these will be discussed in sections \ref{sec:mssm_eventsel_pairs}--\ref{sec:mssm_eventsel_em}.
The optimisation of some of the selections will also be discussed there. Note that 
the optimisations were all based on the dataset collected during the 2015 p-p running period of the \ac{LHC}, which
corresponds to an integrated luminosity of 2.3 fb$^{-1}$.

@@

\subsection{Pair selection and vetos}
\label{sec:mssm_eventsel_pairs}
After applying trigger
requirements, identification criteria and kinematic cuts
more than one possible candidate pair can exist. If
this is the case the pair with the two most isolated candidates
 is chosen, as isolated candidates are less likely 
to be jets misreconstructed
as leptons or hadronic taus.
%If this
%is the case for an event, the pair is chosen as follows:
%\begin{itemize}
%\setlength{\itemsep}{-\baselineskip}
%\item Prefer the pair with most isolated candidate 1 (muon for \mutau and \emu channels,
%electron for \etau channel, either of the $\Pgt_h$s in \tautau channel). For electrons
%and muons this means the object with the smallest relative isolation value is preferred, for $\Pgt_h$s the
%object with raw MVA isolation value nearest to 1.
%\item If the isolation of candidate 1 is the same in both pairs, prefer the pair with highest candidate 1 \pT.
%\item If the \pT~of candidate 1 is the same in both pairs, prefer the pair with most isolated
%candidate 2 (e for the \emu channel, the other $\Pgt_h$ for the \tautau channel, 
%and the $\Pgt_h$ for \etau and \mutau channels).
%\item If the isolation of candidate 2 is the same in both pairs, prefer the pair with highest candidate 2 \pT.
%\end{itemize}

To prevent overlap with other channels, events are rejected
if there are muons and electrons, other than those in the selected pair,
with \pT~$>10$ GeV and passing loose ID and isolation requirements.
This also reduces backgrounds from \WZ events. The application
of these vetos means that the selection of the pair with the
two most isolated candidates is only important where hadronic
taus are concerned, for if there were additional electrons (muons)
the event would not pass the electron (muon) veto.
In addition to these extra electron and muon vetos, \Zee events are 
reduced in the \etau channel by rejecting events
where an opposite--sign pair of electrons of \pT~$>15$ GeV
and passing very loose ID and isolation requirements can be formed. 
In the \mutau channel the contribution from \Zmm events
is reduced in a similar fashion.

@@

This means that $m_{\text{T}}(E_{\text{T}}^{\text{miss}},\Pgt_1^{\text{vis}})$ is equivalent
to the \mT~defined for the \etau and \mutau channels in equation \ref{eqn:hhh_selection_mt}.
The \mTtot~variable provides good separation between signal and QCD multi--jet events
in the \etau, \mutau and \tautau channels, and between
signal and \ttbar events in the \emu channel. These are some of the 
major backgrounds and thus good separation between these processes and 
the signal is important for the sensitivity of the analysis.
The separation between signal and backgrounds is illustrated in figure
\ref{fig:mttot_sigseps}, where figure \ref{fig:mttot_sigseps}a shows the total transverse mass
distribution of the QCD
background in the no b-tag category of the \tautau channel with the gluon fusion
signal at 400 GeV, 1 TeV and 2 TeV overlaid. Figure \ref{fig:mttot_sigseps}b
shows the total transverse mass distribution of the \ttbar background in the b-tag category of the \emu channel with
the b-associated production signal at the same three masses overlaid.

@@

\section{Background estimation}
\label{sec:mssm_bkgs}
There are several backgrounds in this analysis, and the different final
states can have different background compositions. Consider figure \ref{fig:mssm_bkgs_overview}a,
which shows the low $m_{\text{T}}^{\text{tot}}$ region in the no b-tag category
of the \mutau channel and figure \ref{fig:mssm_bkgs_overview}b, which shows the low $m_{\text{T}}^{\text{tot}}$
region in the b-tag category of the \emu channel. These regions are where the backgrounds are concentrated and it
is therefore easier to see the different contributions. \Ztautau is a background in all four channels as 
it has two real taus in the final state, like the signal that we are searching for. 
Smaller backgrounds 
from \Zellell decays also play a role, especially in the \mutau and \etau channels where such events
might pass the selection if for example a jet is misreconstructed as a hadronic tau and only one of the leptons is reconstructed. 
Production of QCD multijet events, labelled `QCD' on the plots in figure \ref{fig:mssm_bkgs_overview}, is a background when 
two jets are misreconstructed as the two particles of the candidate pair. %Relatively likely to happen in tautau channel
As visible in figure \ref{fig:mssm_bkgs_overview}b, the \ttbar background is particularly important in the b-tag category.
This is because top quarks virtually always decay as $\Ptop\rightarrow \PW\Pbottom$, and so such events nearly 
always contain real b-jets. The decay products  of one or both of the \PW bosons, and additional jets in the event, can 
then form \etau, \mutau, \tautau and \emu pairs.\\
The \Wjets process is a background in the \etau and \mutau channels when the lepton from the \PW decay and a jet misreconstructed
as a hadronic tau form a pair. In the \tautau channel it is a background when the \PW decays into $\Pgt\Pgn$ with the tau 
decaying hadronically and an additional jet in the event is misreconstructed as a hadronic tau, or when two jets are
reconstructed as hadronic taus.
In the \emu channel an additional lepton would have to originate from one of the jets, and so in this
channel this background is smaller. Backgrounds that are small in all channels are the di-boson and single-top backgrounds. In 
figures showing the backgrounds the di-boson and single-top backgrounds are drawn together with the \Wjets 
background as the `Electroweak' component.

@@

To estimate these backgrounds a mixture of data-driven 
methods and \ac{MC} samples is employed. The QCD background
is estimated using data-driven techniques in all four channels.
In the \mutau and \etau channels the \Wjets background is also
estimated using data-driven techniques. The control regions used
for the estimation of QCD and \Wjets in the \etau and \mutau channels
are included in a simultaneous fit with the signal region to obtain
the final results. More detail on this is given in section \ref{sec:mssm_sigext_ctrl}.
In the \emu and \tautau channels the \Wjets background is estimated using
\ac{MC} samples. The \Ztautau and \Zellell backgrounds are estimated
using \ac{MC} samples for all four channels. A \Zmm control region
is considered in a simultaneous fit with the signal region to correct and
constrain the \Ztautau normalisation.
The \ttbar, di-boson and single-top backgrounds are estimated
using \ac{MC} samples, with cross-checks in control regions in data.
The rest of this section describes the background estimation methods
in more detail.

@@

\subsubsection{QCD normalisation}
\label{sec:mssm_bkgs_etmt_qcdnorm}
The QCD normalisation is estimated by inverting the opposite-sign requirement
of the di-tau pair in the signal region. The yield is taken from the same--sign
region with otherwise identical cuts to the opposite--sign region. The contributions
from other backgrounds in this region are subtracted to give an estimate of the number
of QCD events in the same--sign region. For all backgrounds apart from \Wjets the
yields to subtract are estimated using \ac{MC} samples. The number of \Wjets events
expected in this region is given by
\begin{equation}\label{eqn:wjets_qcdsub}
N_{\text{W,SS low }m_{\text{T}}} = \frac{N_{\text{MC,SS low }m_{\text{T}}}}{N_{\text{MC,SS high }m_{\text{T}}}}N_{\text{W,SS high }m_{\text{T}}}.
\end{equation}
Because opposite--sign and same--sign QCD events do not
necessarily appear in equal amounts the number of QCD
events obtained by subtracting other backgrounds from the
observed number of events in the same--sign region is multiplied
by $R_{\text{QCD}}^{\text{OS/SS}}$ as derived in section \ref{sec:mssm_bkgs_etmt_qcdosss} 
to obtain an estimate of the number of QCD events in the signal region.
%\subsubsection{Control regions in the fit}
%\label{sec:mssm_bkgs_etmt_ctrl}
%Several control regions in data are used for the estimation
%of the QCD and \Wjets backgrounds: the same--sign and 
%opposite--sign high \mT~regions, as well as the same--sign
%low \mT~region. This leads to three control regions used 
%in each category of both the \mutau and \etau channels to determine
%the initial estimate of the background normalisations.
%These control regions are included in a simultaneous fit
%with the signal regions to obtain the final results. More detail
%can be found in section \ref{sec:mssm_sigext_ctrl}.

@@

\section{Combination procedure}
\label{sec:mssm_combination_procedure}
The idea of combining the two analyses is to combine the 
individual likelihoods to improve the analysis sensitivity and
physics reach. To do this correctly the correlations between
nuisance parameters in the 2015 and 2016 analyses need to be taken into account.

The choice of correlation scheme is decided on
based on the procedure used for the ATLAS and \ac{CMS}
Higgs combinations \cite{MassComb,CouplComb}. This means
uncertainties are either considered 100\% correlated or fully uncorrelated. Partial
correlations are not taken into account, with a small number of exceptions. The
correlations used for this combination are given in table \ref{tab:mssm_combination_correlations},
with the motivation for the chosen correlation given in the third column of the table.
The chosen correlation scheme is motivated
by carefully considering the differences between the two analyses
and the conditions under which they were perofrmed.

%The correct way to establish the correlations is to perform
%dedicated studies into them. In many cases such studies would be 
%unfeasible to perform, or it would not be clear how to approach the 
%problem in the first place.
%Even without performing these studies, a choice of correlation scheme can be motivated
%by carefully considering the differences between the two analyses and the conditions
%under which they were performed.
%This is what has been done for this combination.
%Strictly, studies into the underlying correlations between
%nuisance parameters should be performed. This is however not always
%feasible and in some cases
%The correlation scheme between nuisance parameters relating to the 2015 and 2016
%analyses, as used for this combination, is given in table \ref{tab:mssm_combination_correlations}. 
%The third column of this table gives the motivation for the chosen correlation.

@@

e$\rightarrow\Pgt_{h}$ fake rate & Correlated & Expected to behave the same in 2015 and 2016 datasets, the same anti-electron discriminator was used and the uncertainty on the fake rate should not be affected by the use of a different hadronic tau ID discriminator working point.\\
